BivData Setup

### 2020-03-06 src/BivData_Setup.Rmd
fixed a bug in the IFD calculation for 3CO

@@

#save Rdata
save.image("~./MLH1repo/data/CleanBivData_19.2.20.RData")
#save.image("data/BivData_4_PCA.RData")

>>>>

```{r neg.IFD, echo=FALSE}

#fixed a bug for the multi CO IFD

#source("~./MLH1repo/src/CommonFunc_MLH1repo.R")
#remove IFD
#Curated_BivData <- add_IFD(Curated_BivData)
#t.test.4CO <- Curated_BivData %>% filter(Obj.ID == "8feb17_4jan17_LEW_f1_sp1_3_rev_17")

#neg.IFD <- Curated_BivData[Curated_BivData$IFD1_ABS < 0, ]
#neg.ifd <- Curated_BivData %>% filter(hand.foci.count > 1) %>% filter(IFD3_ABS < 0 )

@@

#save Rdata
save.image("~./MLH1repo/data/CleanBivData_6.3.20.RData")
#save.image("data/BivData_4_PCA.RData")
